Widening income gaps and the shrinking of the middle class

### 2024-04-02 paper/paper.qmd
Added placeholder abstract.

---
title: "Widening income gaps and the shrinking of the middle class"
subtitle: "An analysis of the impact of economic policies on the living standards of middle and lower-income households amidst rising costs and affordability challenges."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class)."
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: ""
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---

>>>>

---
title: "Widening income gaps and the shrinking of the middle class"
subtitle: "An analysis of the impact of economic policies on the living standards of middle and lower-income households amidst rising costs and affordability challenges."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class)."
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: "Over the past five decades, the United States has witnessed a decline in the percentage of adults residing in middle-class households, alongside escalating concerns about housing affordability. This study aims to assess the impact of rising costs on the living standards of middle and lower-income households, recognizing them as the most affected demographic by these economic shifts. Utilizing data from [...], we analyze changes in income distribution and evaluate the influence of economic policy changes, including interest rates and taxation, on the standards of living of these individuals. Additionally, we explore how individual-level characteristics intersect with these policies to address how best to pursue the goal of economic equity across individuals of all backgrounds. We find that [...]."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---
